MSDS6372Project2

### 2021-03-29 MSDS6372Project2.Rmd
update to objective 1

simple.log1 <- glm(income~age+workclass+education+marital.status+occupation+race+sex+capital.loss+hours.per.week+cp.eover7298,family="binomial",data=adult)
summary(simple.log1)
exp(cbind("Odds ratio" = coef(simple.log1), confint.default(simple.log1, level = 0.95)))

@@

>>>>

simple.log1 <- glm(income~age+workclass+education+marital.status+occupation+race+sex+capital.loss+hours.per.week+cp.eover7298,family="binomial",data=adult)
summary(simple.log1)
vif(simple.log1)
exp(cbind("Odds ratio" = coef(simple.log1), confint.default(simple.log1, level = 0.95)))

@@

# Try another model without education since it is not significant
simple.log2 <- glm(income~age+workclass+marital.status+occupation+race+sex+capital.loss+hours.per.week+cp.eover7298,family="binomial",data=adult)
summary(simple.log2)
plot(simple.log2)
fit.pred.sm2<-predict(simple.log2,newdata=adult.test,type="response")

results.sm2 <-prediction(fit.pred.sm2, adult.test$income,label.ordering=c("<=50K.",">50K."))
roc.sm2 = performance(results.sm2, measure = "tpr", x.measure = "fpr")
plot(roc.sm2,colorize = TRUE)
abline(a=0, b= 1)
auc.sm2 <- performance(results.sm2, measure = "auc")
auc.sm2 <- auc.sm2@y.values
text(x = .40, y = .6,paste("AUC = ", round(auc.sm2[[1]],3), sep = ""))
# AUC = 0.892
# Since this dataset is to predict whether income is less than or equal to 50K or greater than 50K
# We want the sensitivity and specificity to be roughly the same - no reasoon to prefer one group or the other
# As we can see from the color legend, the greant to light blue region will give over 80% True positive rate and less than 20% False positive rate
# And that cut off is roughly correspond to 0.275

#Calculate logistic regression using cut of 0.3 on test set
cutoff<-0.26
class.sm2<-factor(ifelse(fit.pred.sm2>cutoff,">50K.","<=50K."),levels=c("<=50K.",">50K."))
confusionMatrix(class.sm2,adult.test$income)
vif(simple.log2)
#Accuracy : 0.8048 Sensitivity : 0.8058 Specificity : 0.8020
```
